### 2015-10-14 paper.tex
Write abstract; resolves #9

\listoftodos

@@

\todo[inline]{Write abstract.}

>>>>

@@

The mechanical power, total rotor drag, and near-wake properties of a 1:6 scale
Reference Model 2 (RM2) were measured in a towing tank. Performance was measured
at multiple Reynolds numbers by varying tow carriage speed, and weak linear
$Re$-dependence was achieved at a turbine diameter Reynolds number $Re_D \approx
10^6$. An optimal tip speed ratio $\lambda_0 = 3.1$ was chosen, at which the
near wake velocity was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity,
turbulence, and mean kinetic energy transport mechanisms were compared and
contrasted with results from a high solidity turbine acquired with the same test
apparatus. Overall, lower levels of streamwise wake recovery were calculated for
the RM2 rotor---a consequence of both the relatively low solidity and tapered
blades. The effects of blade support strut drag on turbine performance were
investigated by covering the rotor's NACA 0021 struts with cylinders. As
expected, this modification drastically reduced rotor power coefficient. Strut
drag was also measured for the NACA 0021 and cylindrical configurations with the
blades removed. These measurements provide a comprehensive open dataset for
validating numerical models' predictive capabilities for low solidity rotors.
